wind_diagrams

### 2019-08-01 Analyses/long_ts.Rmd
2.0
update

site_list_sub <- site_list %>%
  filter(coast == "wc") %>%
  filter(length > 10950)

SACTN_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% site_list_sub$index) %>%
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) 
```

>>>>

site_list_sub <- site_list %>%
  filter(coast == "wc") %>%
  filter(length > 10950) 
# save(site_list_sub, file = "site_list_sub.Rdata")

SACTN_US <- SACTN_daily_v4.2 %>%
  left_join(site_list[,c(4,13)], by = "index") %>%
  filter(index %in% site_list_sub$index) %>%
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE)

save(SACTN_US, file = "Data/SACTN_US.RData")
```

### 2019-08-01 wind_analyses.Rmd
update

# wind_data <- read_csv("Data_P1/wind_data.csv")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay")

@@

>>>>

# wind_data <- read_csv("Data_P1/wind_data.csv")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay", "Hout Bay")

@@

# Matching
  Matching the wind data with the temperature data using the match function

```{r}
match_func <- function(df){
  match <- SACTN_US  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

wind_daily <- wind_daily %>% 
  dplyr::rename(site = temp_sites)

wind_match <- match_func(df = wind_daily)

library(openair)
print(
with(wind_match,
     windRose(data_frame(ws=mean_speed, wd=dir_circ, 
                         date=date, station=factor(site)),

              paddle=FALSE, type="station", width=2))
)
# png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose

# insitu_wind_2 <- insitu_wind %>% 
#   filter(site == "Port Nolloth")
# 
# insitu_wind_3 <- insitu_wind %>% 
#   filter(site == "Lamberts Bay")
# 
# plotPN <- plot(as.factor(format(insitu_wind_2$date, "%Y-%m")), insitu_wind_2$insitu_temp, col = "lightpink")
# plotLB <- plot(as.factor(format(insitu_wind_3$date, "%Y-%m")), insitu_wind_3$insitu_temp, col = "lightpink")
#        
# ?plot
```
